Understanding Factors Contributing to Application Approval in Urban Planning Decisions (2016-2024)

### 2024-12-04 paper/paper.qmd
Final Revision

### Trade-offs
While stratified random sampling ensures proportional representation and enhances the precision of survey estimates, it is not without challenges. One notable trade-off is the complexity involved in defining and managing multiple strata, particularly when the strata are based on multiple dimensions such as application type, planning district, and applicant role. This complexity increases the time and resources required for sample design and execution. For instance, ensuring proportional representation across strata like **Scarborough developers** or **North York consultants** may necessitate oversampling in smaller groups, leading to additional effort in recruitment and logistical coordination.

Another trade-off lies in the potential for overstratification, which can result in small sample sizes within certain strata. If some strata, such as **Scarborough Consent applications**, have very few members, it may be difficult to draw statistically meaningful conclusions. This could necessitate adjustments, such as combining smaller strata or applying post-stratification weighting, which could introduce bias or reduce interpretability. Additionally, the method assumes that the characteristics used to define strata are adequately known and relevant, which may not account for unobserved variables that influence the outcomes, such as the socio-political environment or project complexity. Despite these challenges, the benefits of stratified random sampling in terms of improved accuracy and subgroup analysis make it a robust choice for this study.

@@

Matching survey-reported outcomes with recorded decisions.
Verifying consistency between applicant-reported application details and dataset attributes (e.g., application type, planning district).
To ensure representativeness, response rates would be monitored, and additional recruitment efforts would target underrepresented groups or districts.

@@

- >10 years

@@

Were there any external factors (e.g., economic conditions, policy changes) that influenced the decision?

@@

d[answer box]

>>>>

### Trade-offs
While stratified random sampling ensures proportional representation and enhances the precision of survey estimates, it is not without challenges. One notable trade-off is the complexity involved in defining and managing multiple strata, particularly when the strata are based on multiple dimensions such as application type, planning district, and applicant role. This complexity increases the time and resources required for sample design and execution. For instance, ensuring proportional representation across strata like Scarborough developers or North York consultants may necessitate oversampling in smaller groups, leading to additional effort in recruitment and logistical coordination.

Another trade-off lies in the potential for overstratification, which can result in small sample sizes within certain strata. If some strata, such as Scarborough Consent applications, have very few members, it may be difficult to draw statistically meaningful conclusions. This could necessitate adjustments, such as combining smaller strata or applying post-stratification weighting, which could introduce bias or reduce interpretability. Additionally, the method assumes that the characteristics used to define strata are adequately known and relevant, which may not account for unobserved variables that influence the outcomes, such as the socio-political environment or project complexity. Despite these challenges, the benefits of stratified random sampling in terms of improved accuracy and subgroup analysis make it a robust choice for this study.

@@

Matching survey-reported outcomes with recorded decisions.
Verifying consistency between applicant-reported application details and dataset attributes.
To ensure representativeness, response rates would be monitored, and additional recruitment efforts would target underrepresented groups or districts.

@@

- more than 10 years

@@

Were there any external factors (e.g. economic conditions, policy changes) that influenced the decision?

@@
